Inpainting with controlled dimensionality reduction in the Fourier domain

### 2011-06-21 project/Paper/paper.tex
Paper: Plots to generate.

\subsubsection{Sample data}
We used the three images provided for the last exercise (consisting of both natural and artificial images) to evaluate the accuracy and performance of the chosen parameters. Instead of using the supplied mask, however, we generate one randomly for every evaluation in order to prevent overfitting to a particular mask.

\subsubsection{Found values}
Our observations during the optimization process can be split into three classes:
\begin{itemize}
\item Some parameters converged towards their expected value. The size of the Gaussian kernel, for example, has to be slightly bigger than the largest hole assumed in an image.
\item Some parameters have a clear speed vs. accuracy tradeoff, like the stopping conditions of the threshold optimization, which depend on our cost function and could not be foreseen.
\item Some parameters assumed totally different values than anticipated: The patch size became much larger and the validation set decreased significantly.
\end{itemize}

\section{Results}

 ((( TODO )))

 We compare our algorithm with the following two baseline algorithms:
 \begin{enumerate}
	 \item A simple linear inpainting algorithm using the nearest neighbor pixels.
	 \item A matching pursuit algorithm \cite{matchingpursuit93} with an overcomplete dictionary built with Discrete Cosine transforms.
 \end{enumerate}

  Our algorithm is resistant to high percentages of missing pixels, the average error per missing pixel rises only slowly until ((( TODO level))).

@@

 ((( TODO )))
  Show evidence to support your claims made in the
  introduction.

Organize the results section based on the sequence of table and
figures you include. Prepare the tables and figures as soon as all
the data are analyzed and arrange them in the sequence that best
presents your findings in a logical way. A good strategy is to note,
on a draft of each table or figure, the one or two key results you
want to address in the text portion of the results.
The information from the figures is
summarized in Table~\ref{tab:fourier-wavelet}.

@@

You compare your novel algorithm to \emph{at least two baseline
  algorithms}. For the baselines, you can use the implementations you
developed as part of the programming assignments.

\section{Discussion}
  Discuss the strengths and weaknesses of your
  approach, based on the results. Point out the implications of your  
  novel idea on the application concerned. (((( TODO ))))

\paragraph{Note}
All plots in this paper were created with MATLAB and can be reproduced using the script 'CreatePaperPosts.m' in our submission.\\

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{images/boundaryArtifact_noframe.png}
  \caption{Artifacts that occur without a frame (frame size = 0). The patches are recognizable in the reconstruction}
  \label{fig:boundaryArtifacts}
\end{figure}

@@

\section{Summary}
(((( TODO ))))
  Summarise your contributions in light of the new
  results.

\section*{Acknowledgements}
We would like to recognize and thank the following individuals or groups for their contribution to this work:\\
Our implementation is based on the inpainting and evaluation framework provided by the course "Computer Intelligence Lab" held by Prof. Joachim Buhmann at ETH Zürich.
(((( TODO ))))

@@

>>>>

\subsubsection{Sample data}
We used the three images provided for the last exercise and four additional ones (consisting of both natural and artificial images) to evaluate the accuracy and performance of the chosen parameters. Instead of using the supplied mask, however, we generate one randomly for every evaluation in order to prevent overfitting to a particular mask.

\subsubsection{Found values}
Our observations during the optimization process can be split into three classes:
\begin{itemize}
\item Some parameters converged towards their estimated value. The size of the Gaussian kernel, for example, has to be slightly bigger than the largest hole assumed in an image.
\item Some parameters have a clear speed vs. accuracy tradeoff, like the stopping conditions of the threshold optimization, which depend on our cost function and could not be foreseen.
\item Some parameters assumed totally different values than anticipated: The patch size became much larger and the validation set decreased significantly.
\end{itemize}

\section{Results}
We compared our algorithm with the following three baseline algorithms:
\begin{enumerate}
\item A simple linear inpainting algorithm using the nearest neighbor pixels.
\item A matching pursuit algorithm \cite{matchingpursuit93} with an overcomplete dictionary built with Discrete Cosine transforms.
\item Gaussian interpolation...
\end{enumerate}

@@

Organize the results section based on the sequence of table and
figures you include. Prepare the tables and figures as soon as all
the data are analyzed and arrange them in the sequence that best
presents your findings in a logical way. A good strategy is to note,
on a draft of each table or figure, the one or two key results you
want to address in the text portion of the results.

@@

\paragraph{Note} All plots in this paper were created with MATLAB and can be reproduced using the script \emph{CreatePaperPlots.m} of our submission.

\section{Discussion}
Our algorithm is resistant to high percentages of missing pixels, the average error per missing pixel rises only slowly until ((( TODO level))).

Discuss the strengths and weaknesses of your approach, based on the results. Point out the implications of your novel idea on the application concerned. (((( TODO ))))

\begin{figure}[tbp]
\centering
\includegraphics[width=\columnwidth]{images/boundaryArtifact_noframe.png}
\caption{Artifacts that occur without a frame (frame size = 0). The patches are recognizable in the reconstruction}
\label{boundaryArtifacts}
\end{figure}

@@

\section{Summary}
Summarise your contributions in light of the new results.

\section*{Acknowledgements}
Our implementation is based on the inpainting and evaluation framework provided by the course \emph{Computer Intelligence Lab} held by Prof. Joachim Buhmann at ETH Zurich.

@@

% Plots:
% - threshold optimization => algorithm
% - Framing artifacts (with and w/o frame) => framing
% - Parameter optimization (convergence) => gradient descent
% 
% - Missing pixels vs. error (baselines)
% - stdev over n runs of EvaluateInpainting with rep = 1
% 
% - image with best error (and stdev)
% - image with worst error (and stdev)
% 
% - Bar to illustrate edge reconstruction (patch size)
